%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/macro161/}{\Large Matas Savickis}} & Email : \href{mailto:savickismatas@gmail.com}{savickismatas@gmail.com}\\
  \href{https://github.com/macro161/}{https://github.com/macro161/} & Mobile : +37069068615 \\
  \href{https://www.linkedin.com/in/matas-savickis-669a25134/}{https://www.linkedin.com/in/matas-savickis/}	
\end{tabular*}

\section{Profile}
      	I am a software engineer passionate about applying my knowledge and skills for continuous improvement. 
	My main interest areas are back-end development, micro-services, distributed systems, and functional programming.
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vilnius University Faculty of Mathematics and Informatics }{Vilnius, Lithuania}
      {Bachelor of Software engineering}{2016 - 2020}
  \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Addendum Solutions}{Vilnius, Lithuania}
      {Software developer}{April 2019 - October 2019 (7 months)}
      \resumeItemListStart
        \resumeItem{Project}
          {Developed and maintained  Vilnius waters self-service systems (https://savitarna.vv.lt/login.html).}
        \resumeItem{Back-end}
          {GWT, Java 8, Tomcat, MySQL.}
        \resumeItem{Front-end}
	{HTML, CSS, Javascript.}
      \resumeItemListEnd
    \resumeSubheading
      {Nasdaq}{Vilnius, Lithuania}
      {Software developer}{November 2019 - November 2020 (1 year 1 month)}
      \resumeItemListStart
	 \resumeItem{Project}
	          {Developed Nasdaq Central Securities Depository system for various customers around the globe.}
	 \resumeItem{Back-end}
	          {Java 11, Spring, Java EE, JBoss, JUnit, Mockito, OracleDB, PostgresSQL.}
	 \resumeItem{Front-end}
	          {C\# Windows Form, DevExpress.}
	 \resumeItem{CD/CI}
	          {TeamCity, Docker.}
      \resumeItemListEnd

    \resumeSubheading
      {Oracle}{Vilnius, Lithuania}
      {Software developer}{December 2020 - February 2021 (3 months)}
      \resumeItemListStart
	 \resumeItem{Project}
	          {Oracle Cloud Infrastructure Rover - https://www.oracle.com/cloud/roving-edge-infrastructure/.}
      \resumeItem{Tech stack}
	          {Python, Docker, Gherkin.}
      \resumeItemListEnd
      
       \resumeSubheading
      {EPAM}{Vilnius, Lithuania}
      {Software developer}{March 2021 - January 2022 (11 months)}
      \resumeItemListStart
	  \resumeItem{Project}
	          {Developed SSO system for https://www.vertexinc.com/ using Auth0}
	 \resumeItem{Back-end}
	          {Java 17, Micronaut 3, GraalVM, MySQL, Auth0, Hibernate, AWS SQS}
	 \resumeItem{CD/CI}
	          {Github Actions, Helm Charts, Docker.}
	 \resumeItem{Testing}
	          {JUnit 5, WireMock, Mockito.}
	\resumeItem{Software quality checks}
	          {JaCoCo, PMD, SpotBugs, Checkstyle, SonarQube.}
	\resumeItem{Other activities}
	          {Participated in Junior Java developers' interviewing process.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Front IT}{Vilnius, Lithuania}
      {Software developer}{January 2022 - May 2022 (5 months)}
      \resumeItemListStart
	  \resumeItem{Project}
	          {Perlas POS legacy system maintenance, development, and modernization.}
	 \resumeItem{Back-end}
	          {Java 6 8 11, Hibernate, IBM DB2, Docker.}
	 \resumeItem{CD/CI}
	          {Created CI/CD pipeline using Azure DevOps.}
	 \resumeItem{Testing}
	          {JUnit 5}
	\resumeItem{Other activities}
	          {Participated in Junior Java developers' interviewing process.}
      \resumeItemListEnd
\pagebreak
      \resumeSubheading
      {4Finance}{Vilnius, Lithuania}
      {Software developer}{July 2022 - Present (1 year+)}
      \resumeItemListStart
	  \resumeItem{Project}
	          {Developing short-term loans microservice backend(vivus.lv ondo.lv smscredit.lv vivus.se onea.se).}
	 \resumeItem{Back-end}
	          {Java 17, Spring boot 3, Jakarta EE, Hibernate, PostgreSQL, Docker.}
	 \resumeItem{Front-end}
	          {Vaadin}
	 \resumeItem{CD/CI}
	          {Jenkins, Kibana, Kiali.}
	 \resumeItem{Testing}
	          {Groovy Spock, Wiremock}
	\resumeItem{Other activities.}
	          {Organizing team retro's, mentoring junior developers, working as stand-in Project Owner, implementing async-profiler company-wide for production profiling.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Java 17, SQL, Python, Elixir, TLA+, Javascript, HTML/CSS}
      \hfill
    }
    \item{
	\textbf{Technologies}{: Spring, Jakarta EE, async-profiler, Docker, Micronaut, Git, Hibernate, Apache Tomcat, MySQL,  PostgreSQL}
	\hfil
	}
  \resumeSubHeadingListEnd
%-----------OTHER-----------------
\section{Other}
  \resumeSubHeadingListStart
    \resumeSubItem{Brazilian Jiu-Jitsu}
      {I've been practicing the martial art of Brazilian Jiu-Jitsu for about two and a half years (White belt with three stripes).}
          \resumeSubItem{Powerlifting}
      {Couple days a week I enjoy practicing Powerlifting with my friends at gym.}
    \resumeSubItem{Chess}
      {I casually play chess when I have a free minute or two (FIDE - approx. 1400).}
          \resumeSubItem{Volunteer in "Lietuvos Atgaja" summer camp}
      {In summer of 2017 and 2018 I've spent two weeks in camp "Lietuvos Atgaja", volunteering as a camp counselor.}
  \resumeSubHeadingListEnd
\end{document}