%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/macro161/}{\Large Matas Savickis}} & Email : \href{mailto:savickismatas@gmail.com}{savickismatas@gmail.com}\\
  \href{https://github.com/macro161/}{https://github.com/macro161/} & Mobile : +37069068615 \\
  \href{https://www.linkedin.com/in/matas-savickis-669a25134/}{https://www.linkedin.com/in/matas-savickis/}	
\end{tabular*}

\section{Profile}

      I am a software engineering student seeking full-time position in thefield of software development, where I can apply my knowledge and skills for continuous improvement. My main intrest areas are blockchain technology and low level software development concepts(operating systems, compilers, assembler).
 


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Stasys Šalkauskis gymnasium}{Šiauliai, Lithuania}
      {Secondary education}{2010 - 2015}
    \resumeSubheading
      {Šiauliai 1st Music School}{Šiauliai, Lithuania}
      {Saxophone specialty}{2004 - 2011}
    \resumeSubheading
      {Vilnius University Faculty of Mathematics and Informatics }{Vilnius, Lithuania}
      {Bachelor of Informatics}{2015 - 2016}
    \resumeSubheading
      {Vilnius University Faculty of Mathematics and Informatics }{Vilnius, Lithuania}
      {Bachelor of Software engineering}{2016 - 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Devbridge Group}{Vilnius, Lithuania}
      {Software developer (Sourcery academy internship)}{March 2018 - June 2018}
      \resumeItemListStart
        \resumeItem{React}
          {React is JavaScript library that our team used to create front end for reception application.}
        \resumeItem{ASP.NET Core}
          {This is C\# framework used to create application's back end. Our team used it to create API controllers for data operations.}
        \resumeItem{Entity framework}
          {It is C\# object-relational mapping framework. Our team used it to develop Microsoft SQL Server database.}


      \resumeItemListEnd

    \resumeSubheading
      {Tieto}{Vilnius, Lithuania}
      {Software developer (Month with IT internship)}{Aug 2018 - Sep 2018}
      \resumeItemListStart
        \resumeItem{React native}
          {It is a framework that we used to create front end for Scooter sharing Android application. We use Typescript to develop application.}
        \resumeItem{ASP.NET Core}
          {This is C\# framework used to create application's back end. Our team used it to create API controllers for data operations.}
        \resumeItem{Entity framework}
          {It is C\# object-relational mapping framework. Our team used it to develop Microsoft SQL Server database.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%--------PROJECTS------------
\section{Projects}
  \resumeSubHeadingListStart
    \item{
      \textbf{Operating system model}{: I co-created model of simple operating system writen in C\# (https://github.com/macro161/OS) }
      \hfill
    }
\item{
      \textbf{Reception desk system}{: As a part of Devbridge internship I helped creating deception desk system which helps to inform office staff about people coming to offfice }
      \hfill
    }
\item{
      \textbf{Scooter sharing system}{:As a part of Tieto internship I helped creating mobile application for scooter sharing inside company. System provided ability to track and share scooters in any of Tieto offices worldwide. }
      \hfill
    }
\item{
      \textbf{EmaiLife}{: In development web application which allows to combine social media, chating and emails under one application. EmaiLife will let user to create any number of email account and manage them easily.(https://github.com/macro161/EmaiLife)}
      \hfill
    }
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C\#, Java, Python, Javascript, Typescript, JSON, HTML, CSS, SQL, C++, C, Assembly, JSON, HTML, CSS, LaTeX}
      \hfill
    }
    \item{
	\textbf{Technologies}{: ASP.NET Core, Entity framework, React, React native,  Microsoft SQL Server, Git, Spring, Java EE}
	\hfil
	}
  \resumeSubHeadingListEnd

\section{Languages}
  \resumeSubHeadingListStart
    \item{
      \textbf{Lithuanian}{: Native speaker}
      \hfill
    }
    \item{
	\textbf{English}{: Proficient in spoken and written English}
	\hfil
	}

    \item{
	\textbf{Russian}{: Basic communication skills}
	\hfil
	}
  \resumeSubHeadingListEnd



%-----------OTHER-----------------
\section{Other}
  \resumeSubHeadingListStart
    \resumeSubItem{Volunteer in "Lietuvos Atgaja" summer camp}
      {Every summer since 2017 I spend two weeks in a  summer camp called "Lietuvos Atgaja", volunteering as camp counselor.}
        \resumeSubItem{Lindyhop dancer}
      {I'm an avid dancer, being a member of "lindyhop.lt" club since 2016.}
    \resumeSubItem{Drivers license}
      {Category B drivers license from 2016.}
    \resumeSubItem{Beer brewing experiance}
      {I am brewing beer since 2016. My biggest oreder was to brew 500 liters of variuos types of beer for underground music festival ,,Sound in the vacuume"}
    \resumeSubItem{Chess}
      {My www.lichess.com elo rating is 1300 which put me in the middle of leaderboard.
}   
  \resumeSubHeadingListEnd






\end{document}